Empirical Analysis of Performance Bottlenecks in Graph Neural Network Training and Inference with GPUs

### 2020-12-27 NEUROC/Response-MajRev/response_letter-version2.tex

    \begin{figure}[h]
        \centering
        \subfloat[\texttt{amc}]{\includegraphics[width=0.33\columnwidth]{../figs/experiments/exp_time_comparison_between_training_inference_amazon-computers.pdf}}
        \subfloat[\texttt{amp}]{\includegraphics[width=0.33\columnwidth]{../figs/experiments/exp_time_comparison_between_training_inference_amazon-photo.pdf}}
        \subfloat[\texttt{fli}]{\includegraphics[width=0.33\columnwidth]{../figs/experiments/exp_time_comparison_between_training_inference_flickr.pdf}}
        \caption{Comparison of wall-clock training time and inference time on different datasets.}
        \label{fig:compare_wall_clock_time_of_training_and_inference}
    \end{figure}

@@

    \begin{figure}[h]
            \centering
            \subfloat[\texttt{amp}\label{fig:exp_graphsage_sampling_accuracy_on_amp}]{\includegraphics[width=0.33\columnwidth]{../figs/experiments/exp_graphsage_sampling_accuracy_on_amp.pdf}}
            \subfloat[\texttt{amc}\label{fig:exp_graphsage_sampling_accuracy_on_amc}]{\includegraphics[width=0.33\columnwidth]{../figs/experiments/exp_graphsage_sampling_accuracy_on_amc.pdf}}
            \subfloat[\texttt{fli}\label{fig:exp_graphsage_sampling_accuracy_on_fli}]{\includegraphics[width=0.33\columnwidth]{../figs/experiments/exp_graphsage_sampling_accuracy_on_fli.pdf}}
            \caption{Test accuracy of the neighbor sampler under different batch sizes. FULL means that the full graph participated in the training.}
            \label{fig:exp_sampling_relative_batch_size_accuracy_graphsage}
        \end{figure}

        \begin{figure}[h]
            \centering
            \subfloat[\texttt{amp}\label{fig:exp_cluster_sampling_accuracy_on_amp}]{\includegraphics[width=2in]{../figs/experiments/exp_cluster_sampling_accuracy_on_amp.pdf}}
            %
            \subfloat[\texttt{amc}\label{fig:exp_cluster_sampling_accuracy_on_amc}]{\includegraphics[width=2in]{../figs/experiments/exp_cluster_sampling_accuracy_on_amc.pdf}}
            %
            \subfloat[\texttt{fli}\label{fig:exp_cluster_sampling_accuracy_on_fli}]{\includegraphics[width=2in]{../figs/experiments/exp_cluster_sampling_accuracy_on_fli.pdf}}
            \caption{Test accuracy of the cluster sampler under different batch sizes. FULL means that the full graph participated in the training.}
            \label{fig:exp_sampling_relative_batch_size_accuracy_cluster}
        \end{figure}

### 2020-12-27 NEUROC/sec4-experiments.tex
更新section 4.

For all GNNs, we found that the effects of hyper-parameters on the inference time were the same as the training time.
%
Taking GGNN as an exmple, \figurename~\ref{fig:exp_hyperparameter_on_inference_vertex_edge_phase_time_ggnn} shows the effects of hyper-parameters on inference time of GGNN.
%
By cross-comparing \figurename~\ref{fig:exp_hyperparameter_on_inference_vertex_edge_phase_time_ggnn} and \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}, the trends of inference time and training time were the same: as $dim(\MyVec{h}^1_x)$ increased, the vertex and edge calculation time both grew linearly when $dim(\MyVec{h}^1_x)$ was large enough.
%
For the other GNNs, we observed similar phenomena.
%
The results indicated that the complexity analysis presented in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} were also applicable to inference.

@@

We further measured the effects of the hyper-parameters on the peak GPU memory usage during training in \figurename~\ref{fig:exp_hyperparameter_memory_usage}.
%
The memory usage also increased linearly as the hyper-parameters increased for all GNNs, except for GaAN on $dim(\MyVec{h}^1_x)$.
%
As the hidden vectors $\MyVec{h}^1_x$ in GaAN consumed a small proportion of memory, the growth in the memory usage was not noticeable until $dim(\boldsymbol{h}^1_x)$ was large enough.
%
The effects of the hyper-parameters on inference memory usage were the same as training.
%
Taking GAT as an example, \figurename~\ref{fig:exp_inference_hyperparameter_memory_usage_gat} shows that the peak memory usage during inference grew linearly with the increasing hyper-parameters.
%
By cross-comparing \figurename~\ref{fig:exp_inference_hyperparameter_memory_usage_gat} and \figurename~\ref{fig:exp_hyperparameter_memory_usage_gat}, the hyper-parameters affected the peak memory usage of training and inference in the same way.
%
For the other GNNs, we observed similar phenomena.

>>>>

For all GNNs, we found that the effects of hyper-parameters on the inference time were the same as the training time.
%
Taking GGNN as an exmple, \figurename~\ref{fig:exp_hyperparameter_on_inference_vertex_edge_phase_time_ggnn} shows the effects of hyper-parameters on the inference time of GGNN.
%
By cross-comparing \figurename~\ref{fig:exp_hyperparameter_on_inference_vertex_edge_phase_time_ggnn} and \figurename~\ref{fig:exp_hyperparameter_on_vertex_edge_phase_time_ggnn}, the trends of the inference time and training time were the same: as $dim(\MyVec{h}^1_x)$ increased, the vertex and edge calculation time both grew linearly when $dim(\MyVec{h}^1_x)$ was large enough.
%
For the other GNNs, we observed similar phenomena.
%
The results indicated that the complexity analysis presented in \tablename~\ref{tab:gnn_overview_edge} and \tablename~\ref{tab:gnn_overview_vertex} were also applicable to inference.

@@

We further measured the effects of hyper-parameters on the peak GPU memory usage during training in \figurename~\ref{fig:exp_hyperparameter_memory_usage}.
%
The memory usage also increased linearly as the hyper-parameters increased for all GNNs, except for GaAN on $dim(\MyVec{h}^1_x)$.
%
As the hidden vectors $\MyVec{h}^1_x$ in GaAN consumed a small proportion of memory, the growth in the memory usage was not noticeable until $dim(\boldsymbol{h}^1_x)$ was large enough.
%
The effects of hyper-parameters on the inference memory usage were the same as the training.
%
Taking GAT as an example, \figurename~\ref{fig:exp_inference_hyperparameter_memory_usage_gat} shows that the peak memory usage during inference grew linearly with the increasing hyper-parameters.
%
By cross-comparing \figurename~\ref{fig:exp_inference_hyperparameter_memory_usage_gat} and \figurename~\ref{fig:exp_hyperparameter_memory_usage_gat}, the hyper-parameters affected the peak memory usage of training and inference in the same way.
%
For the other GNNs, we observed similar phenomena.
